### 2019-02-28 papers/journal/encoding.tex
Small fix

\subsubsection{Constraints for stability condition}
%
We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
%
A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m-path$ from node $i$ to node $j$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
It performs enumeration of every $m-path$, $m$-${paths}_i^j$, of at most $w$ length. 
%
Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length $w-1$.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

>>>>

\subsubsection{Constraints for stability condition}
%
We use \texttt{NOracle} to represent the required path to encode the stability condition in VTS.
%
A naive implementation is shown in~\ref{eq:reachbmc1} where \texttt{NOracle}$(m, i, j, w)$ represent the presence of a $m$-$path$ from node $i$ to node $j$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
It performs enumeration of every $m$-$path$, $m$-${paths}_i^j$, of at most $w$ length. 
%
Exploring $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on it, until $m$-${paths}_i^j$ of length $w-1$.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.
